---
title: "Dynamic Model Fit"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: sandstone
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rmarkdown)
library(shiny)
library(shinythemes)
library(flexdashboard)
library(knitr)
library(tools)
library(ggplot2)

#List aesthetics first
```

<style type="text/css">

body {
  font-family: Palatino;
}

.shiny-output-error-validation {
        color: #ff0000;
      }

</style>

<!-- Search Engine Optimization -->
<html>
<head>
<title>Dynamic Fit Index Cutoffs for CFA Models</title>

<meta name="description" content="Derive dynamic fit index cutoffs that are adaptively tailored to the specific factor model and data being evaluated."/>
</head>
</html>

<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src="https://www.googletagmanager.com/gtag/js?id=UA-167733193-2"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'UA-167733193-2');
</script>

```{r design}
fluidPage(theme = shinytheme("sandstone"))

options(shiny.sanitize.errors = FALSE)
```

Sidebar {.sidebar}
=====================================

This app uses equivalence testing to return a range of RMSEA values that can be used to assess model fit for structural equation models.

\  

```{r inputs}
numericInput("sampsize", "Input Sample Size", value=NULL, min=1)

numericInput("chisq", "Input Model Chi-Square", value=NULL, min=.00000001)

numericInput("defre", "Input Model Degrees of Freedom", value=NULL, min=1)

numericInput("chisqb", "Input Baseline Chi-Square", value=NULL, min=.00000001)

numericInput("parms", "Input number of parameters", value=NULL, min=1)

actionButton("go", "Submit")
```

```{r rename}
#Name inputs
N <- eventReactive(input$go,{input$sampsize})
TML <- eventReactive(input$go,{input$chisq})
DF <- eventReactive(input$go,{input$defre})
TMLI <- eventReactive(input$go,{input$chisqb})
P <- eventReactive(input$go,{input$parms})
```

```{r function}
ncp_chi2 <- function(alpha,T_ml,df){
  
  T_ml <- TML()
  df <- DF()
  
  alpha <- .05
  
  z=qnorm(1-alpha)
  z2=z*z 
  z3=z2*z 
  z4=z3*z 
  z5=z4*z
  sig2=2*(2*T_ml-df+2)
  sig=sqrt(sig2)
  sig3=sig*sig2
  sig4=sig2*sig2
  sig5=sig4*sig
  sig6=sig2*sig4
  
  delta=T_ml-df+2+sig*
    (
      z+(z2-1)/sig-z/sig2 + 2*(df-1)*(z2-1)/(3*sig3)
      +( -(df-1)*(4*z3-z)/6+(df-2)*z/2 )/sig4
      +4*(df-1)*(3*z4+2*z2-11)/(15*sig5)
      +(
        -(df-1)*(96*z5+164*z3-767*z)/90-4*(df-1)*(df-2)*(2*z3-5*z)/9
        +(df-2)*z/2
      )/sig6
    )
  
  delta=max(delta,0)
  
  return(delta)
}
```

```{r}
rmsea_results <- eventReactive(input$go,{
  
  n <- N()-1
  T_ml <- TML()
  df <- DF()
  
  #T-size RMSEA#;
  delta_t <- ncp_chi2(.05,T_ml,df)
  RMSEA_t <- sqrt(delta_t/(df*n))
  
  #Recalculate Bins based on Model Characteristics#
  
  RMSEA_e01=exp(
    1.34863-.51999*log(df)+.01925*log(df)*log(df)-.59811*log(n)+.00902*sqrt(n)+.01796*log(df)*log(n))
  
  
  RMSEA_e05=exp(2.06034-.62974*log(df)+.02512*log(df)*log(df)-.98388*log(n)
                +.05442*log(n)*log(n)-.00005188*n+.05260*log(df)*log(n))
  
  
  RMSEA_e08=exp(2.84129-.54809*log(df)+.02296*log(df)*log(df)-.76005*log(n)
                +.10229*log(n)*log(n)-1.11167*(n^.2)+.04845*log(df)*log(n))
  
  
  RMSEA_e10=exp(2.36352-.49440*log(df)+.02131*log(df)*log(df)-.64445*log(n)
                +.09043*log(n)*log(n)-1.01634*(n^.2)+.04422*log(df)*log(n))
  
  
  cutoff=cbind(RMSEA_e01, RMSEA_e05, RMSEA_e08, RMSEA_e10,RMSEA_t)
  cutoff_3=round(cutoff,3)
  
  return(cutoff_3)
})
```

```{r}
cfi_results <- eventReactive(input$go,{
  
  #Parms
  n <- N()-1
  T_ml <- TML()
  df <- DF()
  T_mli <- TMLI()
  p <- P()
  df_i <- p*(p-1)/2
  alpha <- .05
  
  #T-size CFI
  
  delta_t=ncp_chi2(alpha/2, T_ml,df);
  delta_it=ncp_chi2(1-alpha/2, T_mli,df_i);
  CFI_t=1-max(delta_t,0)/max(delta_t,delta_it,0);
  
  ##
  
  CFI_e99=1-exp(
    4.67603-.50827*log(df)+.87087*(df^(1/5))-.59613*((df_i)^(1/5))-1.89602*log(n)
    + .10190*((log(n))^2)+ .03729*log(df)*log(n)
  );
  #corresponding to R-square=.9836;
  
  CFI_e95=1-exp(
    4.12132-.46285*log(df)+.52478*(df^(1/5))-.31832*((df_i)^(1/5))-1.74422*log(n)
    +.13042*((log(n))^2)-.02360*(n^(1/2))+.04215*log(df)*log(n)
  );
  #corresponding to R-square=.9748;
  
  CFI_e92=1-exp(
    6.31234-.41762*log(df)+.01554*((log(df))^2)-.00563*((log(df_i))^2)-1.30229*log(n)
    +.19999*((log(n))^2)-2.17429*(n^(1/5))+.05342*log(df)*log(n)-.01520*log(df_i)*log(n)
  );
  #corresponding to R-square=.9724;
  
  
  CFI_e90=1-exp(
    5.96633-.40425*log(df)+.01384*((log(df))^2)-.00411*((log(df_i))^2)-1.20242*log(n)
    +.18763*((log(n))^2)-2.06704*(n^(1/5))+.05245*log(df)*log(n)-.01533*log(df_i)*log(n)
  );
  #corresponding to R-square=.9713;
  
  cutoff <- cbind(CFI_e90, CFI_e92, CFI_e95, CFI_e99, CFI_t)
  cutoff_3 <- round(cutoff,3)
  
  return(cutoff_3)
})
```

Equivalence Testing
=====================================  

Row {.tabset} 
-----------------------------------------------------------------------

### RMSEA

This is your T-size RMSEA:
<div>
```{r}
renderTable({
  cutoff_3 <- rmsea_results()
  cutoff_3[5]
},
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)
```
</div>

These are the adjusted RMSEA cutoff values derived from equivalence testing:

<div>
```{r fit-table}
#Generate dynamic model fit index cutoffs and table
renderTable({

  #The formula is from Venables 1975 for obtaining the noncentrality #of a non-central chi-square distribution;

cutoff_3 <- rmsea_results()

good <- c("Excellent:","Close:","Fair:","Mediocre:","Poor:")

one <- paste(cutoff_3[1],"or below")
two <- paste(cutoff_3[1],"to",cutoff_3[2])
three <- paste(cutoff_3[2],"to",cutoff_3[3])
four <- paste(cutoff_3[3],"to",cutoff_3[4])
five <- paste(cutoff_3[4],"or above")

vals <- rbind(one,two,three,four,five)

as.data.frame(cbind(good,vals))
  },
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)

```
</div>

### CFA

This is your T-size CFI:
<div>
```{r}
renderTable({
  cutoff_3 <- cfi_results()
  cutoff_3[5]
},
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)
```
</div>

### Figure

This is a plot comparing your T-size RMSEA value to the adjusted RMSEA cutoff values derived from equivalence testing:

```{r}
renderPlot({
  cutoff_3 <- rmsea_results()
  
  e <- max(cutoff_3[4],cutoff_3[5])
  e

  x <- cutoff_3[1:4]
  x
  
  m <- e+(cutoff_3[1]-0)
  m
  
  ex <- mean(c(.00001,x[1]))
  cl <- mean(c(x[1],x[2]))
  fa <- mean(c(x[2],x[3]))
  me <- mean(c(x[3],x[4]))
  po <- mean(c(x[4],m))
  
  ggplot(data.frame(x), aes(x=x, y=0)) +
    geom_point(alpha=0)  +
    annotate("segment",x=0,xend=m, y=0, yend=0, size=1,col="grey50") +
    annotate("segment",x=0,xend=0, y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=m,xend=m, y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[1],xend=x[1], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[2],xend=x[2], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[3],xend=x[3], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[4],xend=x[4], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=cutoff_3[5],xend=cutoff_3[5],y=-0.1,yend=.3, size=1, col="tomato4")+
    annotate("text",x=cutoff_3[5],y=.6,label=paste("T-size \n RMSEA \n",cutoff_3[5]),
             col="tomato4", size=4.5)+
    annotate("text",x=ex,y=-.5,label="Excellent",size=4.5)+
    annotate("text",x=cl,y=-.5,label="Close",size=4.5)+
    annotate("text",x=fa,y=-.5,label="Fair",size=4.5)+
    annotate("text",x=me,y=-.5,label="Mediocre",size=4.5)+
    annotate("text",x=po,y=-.5,label="Poor",size=4.5)+
    geom_text(aes(label = x),col="grey20", position=position_nudge(y=-.2),size=4.5) +
    scale_x_continuous(limits = c(0,m)) +
    scale_y_continuous(limits = c(-1,1)) +
    scale_color_manual(values = unname(colours)) + 
    theme(panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank())
})
```


### References

To cite the ideas behind dynamic fit index cutoff values:

- [McNeish, D.](https://sites.google.com/site/danielmmcneish/home) & [Wolf, M. G.](https://www.melissagwolf.com/) (2020, July 7). Dynamic Fit Index Cutoffs for Confirmatory Factor Analysis Models. https://doi.org/10.31234/osf.io/v8yru

    - *Paper is currently under review*

To cite the values generated by this app:

- [Wolf, M. G.](https://www.melissagwolf.com/) & [McNeish, D.](https://sites.google.com/site/danielmmcneish/home) (2020). Dynamic Model Fit. R Shiny application version 1.0.1.

    - *An accompanying R package is under development*
    
The equivalence testing method for structural equation modeling was introduced by Yuan, et. al.  The code to generate the T-size RMSEA was provided by the authors and can be accessed [here](https://www3.nd.edu/~kyuan/EquivalenceTesting/T-size_RMSEA_CFI.R).  To cite the equivalence testing method:

- Yuan, K.-H., Chan, W., Marcoulides, G. A., & Bentler, P. M. [(2016)](https://www.researchgate.net/publication/283805905_Assessing_Structural_Equation_Models_by_Equivalence_Testing_With_Adjusted_Fit_Indexes). Assessing structural equation models by equivalence testing with adjusted fit indexes. *Structural Equation Modeling, 23*(3), 319–330.
