---
title: "Dynamic Model Fit"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: sandstone
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rmarkdown)
library(shiny)
library(shinythemes)
library(flexdashboard)
library(knitr)
library(tools)
library(ggplot2)

#List aesthetics first
```

<style type="text/css">

body {
  font-family: Palatino;
}

.shiny-output-error-validation {
        color: #ff0000;
      }

</style>

<!-- Search Engine Optimization -->
<html>
<head>
<title>Dynamic Fit Index Cutoffs for CFA Models</title>

<meta name="description" content="Derive dynamic fit index cutoffs that are adaptively tailored to the specific factor model and data being evaluated."/>
</head>
</html>

<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src="https://www.googletagmanager.com/gtag/js?id=UA-167733193-2"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'UA-167733193-2');
</script>

```{r design}
fluidPage(theme = shinytheme("sandstone"))

options(shiny.sanitize.errors = FALSE)
```

Sidebar {.sidebar}
=====================================

This app uses equivalence testing to return a range of RMSEA and CFI values that can be used to assess model fit for structural equation models.

\  

```{r inputs}
numericInput("sampsize", "Input Sample Size", value=NULL, min=1)

numericInput("chisq", "Input Model Chi-Square", value=NULL, min=.00000001)

numericInput("defre", "Input Model Degrees of Freedom", value=NULL, min=1)

numericInput("parms", "Input Number of Observed Variables", value=NULL, min=1)

numericInput("chibase", "Input Baseline Chi-Square", value=NULL, min=.00000001)

actionButton("go", "Submit")
```

```{r rename}
#Name inputs
N <- eventReactive(input$go,{input$sampsize})
TML <- eventReactive(input$go,{input$chisq})
DF <- eventReactive(input$go,{input$defre})
TML_I <- eventReactive(input$go,{input$chibase})
P <- eventReactive(input$go,{input$parms})
```

```{r function}
ncp_chi2 <- function(alpha,T_ml,df){
  
  z=qnorm(1-alpha)
  z2=z*z 
  z3=z2*z 
  z4=z3*z 
  z5=z4*z
  sig2=2*(2*T_ml-df+2)
  sig=sqrt(sig2)
  sig3=sig*sig2
  sig4=sig2*sig2
  sig5=sig4*sig
  sig6=sig2*sig4
  
  delta=T_ml-df+2+sig*
    (
      z+(z2-1)/sig-z/sig2 + 2*(df-1)*(z2-1)/(3*sig3)
      +( -(df-1)*(4*z3-z)/6+(df-2)*z/2 )/sig4
      +4*(df-1)*(3*z4+2*z2-11)/(15*sig5)
      +(
        -(df-1)*(96*z5+164*z3-767*z)/90-4*(df-1)*(df-2)*(2*z3-5*z)/9
        +(df-2)*z/2
      )/sig6
    )
  
  delta=max(delta,0)
  
  return(delta)
}
```

```{r}
results <- eventReactive(input$go,{

  p <- P()
  T_ml <- TML()
  df <- DF()
  T_mli <- TML_I()
  n <- N()-1
  df_i <- p*(p-1)/2
  alpha <- .05
  
  #T-size RMSEA#;
  delta_t_r <- ncp_chi2(alpha,T_ml,df)
  RMSEA_t <- sqrt(delta_t_r/(df*n))
  
  #T-size CFI
  
  delta_t_c <- ncp_chi2(alpha/2, T_ml,df)
  delta_it <- ncp_chi2(1-alpha/2, T_mli,df_i)
  CFI_t <- 1-max(delta_t_c,0)/max(delta_t_c,delta_it,0)
  
  #Recalculate Bins based on Model Characteristics - RMSEA#
  
  RMSEA_e01=exp(
    1.34863-.51999*log(df)+.01925*log(df)*log(df)-.59811*log(n)+.00902*sqrt(n)+.01796*log(df)*log(n))
  
  
  RMSEA_e05=exp(2.06034-.62974*log(df)+.02512*log(df)*log(df)-.98388*log(n)
                +.05442*log(n)*log(n)-.00005188*n+.05260*log(df)*log(n))
  
  
  RMSEA_e08=exp(2.84129-.54809*log(df)+.02296*log(df)*log(df)-.76005*log(n)
                +.10229*log(n)*log(n)-1.11167*(n^.2)+.04845*log(df)*log(n))
  
  
  RMSEA_e10=exp(2.36352-.49440*log(df)+.02131*log(df)*log(df)-.64445*log(n)
                +.09043*log(n)*log(n)-1.01634*(n^.2)+.04422*log(df)*log(n))
  
  ## Recalculate - CFI
  
  CFI_e99=1-exp(
    4.67603-.50827*log(df)+.87087*(df^(1/5))-.59613*((df_i)^(1/5))-1.89602*log(n)
    + .10190*((log(n))^2)+ .03729*log(df)*log(n)
  );
  #corresponding to R-square=.9836;
  
  CFI_e95=1-exp(
    4.12132-.46285*log(df)+.52478*(df^(1/5))-.31832*((df_i)^(1/5))-1.74422*log(n)
    +.13042*((log(n))^2)-.02360*(n^(1/2))+.04215*log(df)*log(n)
  );
  #corresponding to R-square=.9748;
  
  CFI_e92=1-exp(
    6.31234-.41762*log(df)+.01554*((log(df))^2)-.00563*((log(df_i))^2)-1.30229*log(n)
    +.19999*((log(n))^2)-2.17429*(n^(1/5))+.05342*log(df)*log(n)-.01520*log(df_i)*log(n)
  );
  #corresponding to R-square=.9724;
  
  
  CFI_e90=1-exp(
    5.96633-.40425*log(df)+.01384*((log(df))^2)-.00411*((log(df_i))^2)-1.20242*log(n)
    +.18763*((log(n))^2)-2.06704*(n^(1/5))+.05245*log(df)*log(n)-.01533*log(df_i)*log(n)
  );
  
  ##
  
  
  cutoff_rmsea <- cbind(RMSEA_e01, RMSEA_e05, RMSEA_e08, RMSEA_e10, RMSEA_t)
  cutoff_cfi <- cbind(CFI_e90, CFI_e92, CFI_e95, CFI_e99, CFI_t)
  cutoff_combo <- rbind(cutoff_rmsea,cutoff_cfi)
  cutoff_3 <- round(cutoff_combo,3)
  colnames(cutoff_3) <- c("Cut_1","Cut_2","Cut_3","Cut_4","T")
  
  return(cutoff_3)
})
```

Equivalence Testing
=====================================  

Row {.tabset} 
-----------------------------------------------------------------------

### Instructions

To use the equivalence testing method to compute adjusted RMSEA and CFI values and the corresponding adjusted cutoff values, you will need five pieces of information.

1) Your sample size.
2) Your model's chi-square value.
      - In AMOS, this is the Chi-Square value under Notes for Model.  This value can also be found under Model Fit in the CMIN box, in the cell at the intersection of Default model and CMIN.
      - In MPlus, this is the value under Chi-Square Test of Model Fit.
      - In jamovi, this is the chi-square value under Test for Exact Fit.
      - In LISREL, this is the Maximum Likelihood Ratio Chi-Square under the Goodness of Fit Statistics.
      - In lavaan (R), this is the value under chisq from the fitMeasures function.
3) Your model's degrees of freedom.
4) The number of observed variables in your model.  These are the number of squares on your path diagram.
5) The chi-square for the baseline model.  This value is only necessary to compute the values for the CFI.  If you do not include it, the app will still print the RMSEA values.
      - In AMOS, this value can be found under Model Fit in the CMIN box, in the cell at the intersection of Independence model and CMIN.
      - In MPlus, this is the value under Chi-Square Test of Model Fit for the Baseline Model.
      - At this time, we do not believe that jamovi returns this value.
      - In LISREL, this is the Chi-Square for Independence Model under the Goodness of Fit Statistics.
      - In lavaan (R), this is the value under baseline.chisq from the fitMeasures function.
      
Press Submit when you are done.  The results will appear in the RMSEA and CFI tabs.

### RMSEA

This is your T-size RMSEA:
<div>
```{r}
renderTable({
  cut <- results()
  cut[1,5]
},
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)
```
</div>

These are the adjusted RMSEA cutoff values derived from equivalence testing:

<div>
```{r fit-table-rmsea}
#Generate dynamic model fit index cutoffs and table
renderTable({

  #The formula is from Venables 1975 for obtaining the noncentrality #of a non-central chi-square distribution;

cut <- results()

good <- c("Excellent:","Close:","Fair:","Mediocre:","Poor:")

one_r <- paste(cut[1,1],"or below")
two_r <- paste(cut[1,1],"to",cut[1,2])
three_r <- paste(cut[1,2],"to",cut[1,3])
four_r <- paste(cut[1,3],"to",cut[1,4])
five_r <- paste(cut[1,4],"or above")

vals_r <- rbind(one_r,two_r,three_r,four_r,five_r)

as.data.frame(cbind(good,vals_r))
  },
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)

```
</div>

This is a plot comparing your T-size RMSEA value to the adjusted RMSEA cutoff values derived from equivalence testing:

<div>
```{r}
renderPlot({
  cut <- results()
  
  e <- max(cut[1,4],cut[1,5])
  e

  x <- cut[1,1:4]
  x
  
  m <- e+(cut[1,1]-0)
  m
  
  ex <- mean(c(.00001,x[1]))
  cl <- mean(c(x[1],x[2]))
  fa <- mean(c(x[2],x[3]))
  me <- mean(c(x[3],x[4]))
  po <- mean(c(x[4],m))
  
  ggplot(data.frame(x), aes(x=x, y=0)) +
    geom_point(alpha=0)  +
    annotate("segment",x=0,xend=m, y=0, yend=0, size=1,col="grey50") +
    annotate("segment",x=0,xend=0, y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=m,xend=m, y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[1],xend=x[1], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[2],xend=x[2], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[3],xend=x[3], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[4],xend=x[4], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=cut[1,5],xend=cut[1,5],y=-0.1,yend=.25, size=1, col="tomato4")+
    annotate("text",x=cut[1,5],y=.6,label=paste("T-size \n RMSEA \n",cut[1,5]),
             col="tomato4", size=4.5)+
    annotate("text",x=ex,y=-.5,label="Excellent",size=4.5)+
    annotate("text",x=cl,y=-.5,label="Close",size=4.5)+
    annotate("text",x=fa,y=-.5,label="Fair",size=4.5)+
    annotate("text",x=me,y=-.5,label="Mediocre",size=4.5)+
    annotate("text",x=po,y=-.5,label="Poor",size=4.5)+
    geom_text(aes(label = x),col="grey20", position=position_nudge(y=-.2),size=4.5) +
    scale_x_continuous(limits = c(0,m)) +
    scale_y_continuous(limits = c(-1,1)) +
    scale_color_manual(values = unname(colours)) + 
    theme(panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank())
}, width=800,height = 200)
```
</div>

### CFA

This is your T-size CFI:
<div>
```{r}
renderTable({
  cut <- results()
  cut[2,5]
},
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)
```
</div>

These are the adjusted CFI cutoff values derived from equivalence testing:

<div>
```{r fit-table-cfi}
#Generate dynamic model fit index cutoffs and table
renderTable({

  #The formula is from Venables 1975 for obtaining the noncentrality #of a non-central chi-square distribution;

cut <- results()

good <- c("Excellent:","Close:","Fair:","Mediocre:","Poor:")

one_c <- paste(cut[2,1],"or below")
two_c <- paste(cut[2,1],"to",cut[2,2])
three_c <- paste(cut[2,2],"to",cut[2,3])
four_c <- paste(cut[2,3],"to",cut[2,4])
five_c <- paste(cut[2,4],"or above")

vals_c <- rbind(five_c,four_c,three_c,two_c,one_c)

as.data.frame(cbind(good,vals_c))
  },
    digits=3, align='l', colnames = FALSE, width="auto",
    bordered = TRUE)

```
</div>

This is a plot comparing your T-size CFI value to the adjusted CFI cutoff values derived from equivalence testing:

<div>
```{r}
renderPlot({
  cut <- results()
  
  e <- min(cut[2,1],cut[2,5])
  e
  
  x <- cut[2,1:4]
  x
  
  m <- e-(1-cut[2,4])
  m
  
  ex <- mean(c(1,x[4]))
  cl <- mean(c(x[4],x[3]))
  fa <- mean(c(x[3],x[2]))
  me <- mean(c(x[2],x[1]))
  po <- mean(c(x[1],m))
  
  ggplot(data.frame(x), aes(x=x, y=0)) +
    geom_point(alpha=0)  +
    annotate("segment",x=m,xend=1, y=0, yend=0, size=1,col="grey50") +
    annotate("segment",x=1,xend=1, y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=m,xend=m, y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[1],xend=x[1], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[2],xend=x[2], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[3],xend=x[3], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=x[4],xend=x[4], y=-0.1,yend=0.1, size=1,col="grey50") +
    annotate("segment",x=cut[2,5],xend=cut[2,5],y=-0.1,yend=.25, size=1, col="tomato4")+
    annotate("text",x=cut[2,5],y=.6,label=paste("T-size \n CFI \n",cut[2,5]),
             col="tomato4", size=4.5)+
    annotate("text",x=ex,y=-.5,label="Excellent",size=4.5)+
    annotate("text",x=cl,y=-.5,label="Close",size=4.5)+
    annotate("text",x=fa,y=-.5,label="Fair",size=4.5)+
    annotate("text",x=me,y=-.5,label="Mediocre",size=4.5)+
    annotate("text",x=po,y=-.5,label="Poor",size=4.5)+
    geom_text(aes(label = x),col="grey20", position=position_nudge(y=-.2),size=4.5) +
    scale_x_continuous(limits = c(m,1)) +
    scale_y_continuous(limits = c(-1,1)) +
    scale_color_manual(values = unname(colours)) + 
    theme(panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank())
}, width=800,height = 200)
```
</div>

### References

To cite the equivalence testing method:

- Yuan, K.-H., Chan, W., Marcoulides, G. A., & Bentler, P. M. [(2016)](https://www.researchgate.net/publication/283805905_Assessing_Structural_Equation_Models_by_Equivalence_Testing_With_Adjusted_Fit_Indexes){target="_parent"}. Assessing structural equation models by equivalence testing with adjusted fit indexes. *Structural Equation Modeling, 23*(3), 319–330.
- Marcoulides, K. M. & Yuan, K.-H. [(2017)](https://www.tandfonline.com/doi/abs/10.1080/10705511.2016.1225260){target="_parent"}. New ways to evaluate goodness of fit: A note on using equivalence testing to assess structural equation models. *Structural Equation Modeling, 24*(1), 148-153.

    - *The code used in this app was provided by the authors of these papers and can be accessed* [here](https://www3.nd.edu/~kyuan/EquivalenceTesting/T-size_RMSEA_CFI.R){target="_parent"}, [here](https://www3.nd.edu/~kyuan/EquivalenceTesting/RMSEA_e.R){target="_parent"}, *and* [here](https://www3.nd.edu/~kyuan/EquivalenceTesting/CFI_e.R){target="_parent"}.  

To cite the values generated by this app:

- [Wolf, M. G.](https://www.melissagwolf.com/){target="_parent"} & [McNeish, D.](https://sites.google.com/site/danielmmcneish/home){target="_parent"} (2020). Dynamic Model Fit. R Shiny application version 1.1.0.

    - [*R Package (beta)*](https://github.com/melissagwolf/dynamic){target="_parent"}
    
<span style="color: #93002D;">Please submit bug reports to [Melissa Wolf](mailto:melissagordon@ucsb.edu).</span>

